\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{cerulean}
\usepackage[hmargin=0.5in,vmargin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\name{Ali}{Sajid Imami}
\address{2050 Country Trace Pl, Apt 3C}{Toledo, OH 43616}{USA}
\phone[mobile]{+1~(567)~698~3744}
\email{Ali.Sajid.Imami@gmail.com}
\email{Ali.Imami@rockets.utoledo.edu}
\homepage{www.aliimami.com}
\social[linkedin]{asimami}
\social[github]{AliSajid}
\social[orcid]{0000-0003-3684-3539}

\begin{document}

\makecvtitle

\section{Education \& Honors}
\cventry{2022--Present}{Ph.D. Candidate, Bioinformatics}{University of Toledo, College of Medicine and Life Sciences, Department of Neurosciencs and Psychiatry}{Toledo, OH}{}{Fulbright Scholar (M.S.)}
\cventry{2020--2022}{M.S. Bioinformatics}{University of Toledo}{Toledo, OH}{}{Fulbright-funded thesis}
\cventry{2007--2012}{MB~BS (Medicine)}{Nishtar Medical University}{Multan, Pakistan}{}{Direct-entry medical degree}

\section{Research \& Publications}
\cvitem{Selected Publications}{
\begin{itemize}
    \item Creeden, J., \textbf{Imami, A. S.}, Eby, H. M., Gillman, C., Becker, K. N., Reigle, J., Andari, E., Pan, Z. K., O’Donovan, S. M., McCullumsmith, R. E., \& McCullumsmith, C. B. (2020). Fluoxetine as an Anti-Inflammatory Therapy in SARS-CoV-2 Infection. SSRN Electronic Journal. \url{https://doi.org/10.2139/ssrn.3736012}
    \item Di Re, J., Marini, M., Hussain, S. I., Singh, A. K., Venkatesh, A., Alshammari, M. A., Alshammari, T. K., Hamoud, A.-R. A., Imami, A. S., Haghighijoo, Z., Fularcyzk, N., Stertz, L., Hawes, D., Mosebarger, A., Jernigan, J., Chaljub, C., Nehme, R., Walss-Bass, C., Schulmann, A., … Laezza, F. (2025). $\beta$IV spectrin abundancy, cellular distribution and sensitivity to AKT/GSK3 regulation in schizophrenia. Molecular Psychiatry, 30(7), 3090–3102. \url{https://doi.org/10.1038/s41380-025-02917-1}
    \item Imami, A. S., McCullumsmith, R. E., \& O’Donovan, S. M. (2021). Strategies to identify candidate repurposable drugs: COVID-19 treatment as a case example. Translational Psychiatry, 11(1), 591. \url{https://doi.org/10.1038/s41398-021-01724-w}
    \item Imami, A. S., O’donovan, S. M., Creeden, J. F., Wu, X., Eby, H., McCullumsmith, C. B., Uvnäs-Moberg, K., McCullumsmith, R. E., \& Andari, E. (2020). Oxytocin’s anti-inflammatory and proimmune functions in covid-19: A transcriptomic signature-based approach. Physiological Genomics. \url{https://doi.org/10.1152/physiolgenomics.00095.2020}
    \item Ryan, W. G., Eby, H. M., Bearss, N. R., Imami, A. S., Hamoud, A., Pulvender, P., Bollinger, J. L., Wohleb, E. S., \& McCullumsmith, R. E. (2025). Characterization of active kinase signaling pathways in astrocytes and microglia. Cold Spring Harbor Laboratory. \url{https://doi.org/10.1101/2025.04.18.649617}
\end{itemize}
Additional publications available upon request.
}

\section{Open–Source Tools \& Projects}
\cvitem{}{
\begin{itemize}
    \item \textbf{KINNET}: Kinase INteraction NETwork, an R package for infering kinase interaction networks from PamChip data
    \item \textbf{drugfindR}: An R package for automated and high throughput screening of repurposable drugs using the LINCS database
    \item \textbf{BioPathNet}: An infrastructure R package that provides an interface for the \emph{3PodR} Pipeline
    \item \textbf{aaprop}: An online REST API for accessing amino acid information
    \item \textbf{Variant Forge}: Application to quantify the physicochemical distances between protein or amino acid sequences
\end{itemize}
}

\section{Professional Experience}
\cventry{2022--Present}{Graduate Research Assistant}{University of Toledo, COMLS}{Toledo, OH}{}{
\begin{itemize}
\item Led design and implementation of bioinformatics pipelines for schizophrenia research.
\item Co-authored peer-reviewed articles; presented findings at GLBIO 2024.
\item Mentored 5 junior researchers in computational methods.
\end{itemize}
}

\section{Community Service}
\cventry{2021--2022}{President, Graduate Student Association}{University of Toledo}{Toledo, OH}{}{
\begin{itemize}
\item Advocated for graduate student funding and visibility.
\item Organized career workshops and research symposiums.
\end{itemize}
}

\section{Teaching, Outreach \& Volunteering}
\cvitem{}{
\begin{itemize}
\item Taught Rust, R, Bayesian stats, and cloud computing at 4 hackathons and workshops.
\item Co-designed a mental-health survey platform; volunteered at local clinics.
\item Guest lecturer on bioinformatics and mental health data analytics.
\end{itemize}
}

\section{Skills}
\cvdoubleitem{Languages}{Python, R, Rust}{Tools}{Docker, Kubernetes, AWS, GCP}
\cvdoubleitem{Methods}{Multi-omics integration, kinase-network modeling}{Other}{Scientific writing, public speaking}

\section{Professional Affiliations}
\cvitem{Member}{Society for Neuroscience}
\cvitem{Member}{International Society for Computational Biology}

\end{document}
