\section{Community Service \& Activism}

\cventry{2022--2023}{President}{Council of Biomedical Graduate Students}{Toledo, OH}{}{
    \begin{itemize}
        \item Led advocacy initiatives for biomedical graduate students.
        \item Liaised with university administration to address student concerns.
        \item Organized seasonal events for incoming and current students, including the Lab Coat Ceremony.
    \end{itemize}
}

\cventry{2021--2022}{President}{Graduate Student Association, University of Toledo}{Toledo, OH}{}{
    \begin{itemize}
        \item Advocated for increased graduate student funding and visibility.
        \item Organized career development workshops and research symposiums.
        \item Successfully negotiated with administration to resolve graduate student concerns regarding parking fees and space availability.
    \end{itemize}
}

\cventry{2021--2023}{Founding President}{Association of Bioinformaticists and Computational Biologists}{Toledo, OH}{}{
    \begin{itemize}
        \item Founded the University of Toledo's first student organization for computational biology/bioinformatics.
        \item Hosted workshops and networking events for graduate students.
        \item Launched an annual regional bioinformatics hackathon.
    \end{itemize}
}

\cventry{2021--2022}{Vice President}{Council of Biomedical Graduate Students}{Toledo, OH}{}{
    \begin{itemize}
        \item Supported presidential initiatives and led student advocacy efforts.
        \item Strengthened communication between students and faculty.
        \item Helped plan year-round programming for graduate students.
        \item Successfully opposed and reversed a policy that would have docked graduate student pay for minor administrative errors.
    \end{itemize}
}

\cventry{2011--2013}{Founder \& President}{Irrtiqa}{Multan, Pakistan}{}{
    \begin{itemize}
        \item Led seminars on rationality and skepticism, titled *How to Change Your Thinking*.
        \item Conducted youth leadership camps to foster critical thinking and civic responsibility.
        \item Organized debate and essay competitions on citizenship and democracy for high school students.
    \end{itemize}
}

\cventry{2010--2013}{Founder \& President}{TEACH}{Multan, Pakistan}{}{
    \begin{itemize}
        \item Developed a presentation series titled *Human Rights Throughout the Ages*, tracing the development of the Universal Declaration of Human Rights.
        \item Delivered the series across schools and colleges in the region.
        \item Promoted human rights awareness and civic engagement through education.
    \end{itemize}
}

\cventry{2016--Present}{Director of Information Technology}{Council for Democracy and Tolerance}{Fairfax, VA}{}{
    \begin{itemize}
        \item Oversee IT infrastructure and digital tools for a U.S.-based democracy and tolerance advocacy organization.
        \item Implement cloud-based solutions to support distributed collaboration, including email, document management, and automated backups.
        \item Lead data analysis efforts for quarterly performance reviews of organizational initiatives.
    \end{itemize}
}

\cventry{2016--2021}{Chief Technology Officer}{The Joy of Urdu}{Lahore, Pakistan}{}{
    \begin{itemize}
        \item Directed technology strategy for a growing, decentralized nonprofit promoting Urdu literature and culture.
        \item Supported a 10-person distributed team by standardizing software use, managing licenses and access, and overseeing digital onboarding.
        \item Architected and maintained a redundant AWS-based WordPress infrastructure to ensure reliable content delivery.
    \end{itemize}
}

\cventry{2017}{Founding Member \& IT Consultant}{Alliance of Inclusive Muslims}{}{}{
    \begin{itemize}
        \item Participated in the founding conference as a representative of *Muslim World Today*.
        \item Developed a resilient and redundant website for the organization.
        \item Built a distributed internal IT system using GSuite for a remote team.
        \item Provided IT capacity-building support to member organizations.
    \end{itemize}
}
