\section{Professional Experience}

\cventry{2020--Present}{Graduate Research Assistant}{Cognitive Disorders Research Lab, University of Toledo}{Toledo, OH}{}{
    \begin{itemize}
        \item Led research on kinase network inference and drug repurposing in schizophrenia; co-authored 25+ peer-reviewed publications and presented at 10+ national conferences.
        \item Supervised the Schizophrenia Research Team, overseeing 8 published manuscripts during tenure.
        \item Designed and deployed lab-wide AWS infrastructure supporting 50+ researchers with scalable compute and secure access to research tools.
        \item Principal developer of three internal pipelines for transcriptomic and proteomic data analysis, significantly reducing analysis time and error rates.
        \item Mentored 5 junior researchers in computational methods, code quality, and reproducible research practices.
    \end{itemize}
}

\cventry{2017--2018}{Deputy Medical Superintendent / Medical Officer}{Chaudhary Pervaiz Elahi Institute of Cardiology}{Multan, Pakistan}{}{
    \begin{itemize}
        \item Supported hospital administration by coordinating operational reviews, resource allocation, and logistics.
        \item Oversaw the hospital's dengue screening program for six months, ensuring continuity of services during peak season.
        \item Led the development of the hospital's official introduction and history video as part of a visibility and outreach initiative.
    \end{itemize}
}

\cventry{2016--2021}{Chief Technology Officer}{The Joy of Urdu}{Lahore, Pakistan}{}{
    \begin{itemize}
        \item Directed technology strategy for a growing, decentralized nonprofit promoting Urdu literature and culture.
        \item Supported a 10-person distributed team by standardizing software use, managing licenses and access, and overseeing digital onboarding.
        \item Architected and maintained a redundant AWS-based WordPress infrastructure to ensure reliable content delivery.
    \end{itemize}
}

\cventry{2016--Present}{Director of Information Technology}{Council for Democracy and Tolerance}{Fairfax, VA}{}{
    \begin{itemize}
        \item Oversee IT infrastructure and digital tools for a U.S.-based democracy and tolerance advocacy organization.
        \item Implement cloud-based solutions to support distributed collaboration, including email, document management, and automated backups.
        \item Lead data analysis efforts for quarterly performance reviews of organizational initiatives.
    \end{itemize}
}

\cventry{2015--2016}{House Officer}{Nishtar Hospital}{Multan, Pakistan}{}{
    \begin{itemize}
        \item Delivered direct patient care in medical and surgical rotations, including ER and ICU assignments.
        \item Participated in daily rounds, treatment planning, and emergency care coordination.
    \end{itemize}
}

\cventry{2014--2016}{Chief Technology Officer}{Khabaristan Times}{Lahore, Pakistan}{}{
    \begin{itemize}
        \item Built and maintained a secure, auto-scaling AWS-backed platform for a satirical news outlet dubbed the "Onion of Pakistan."
        \item Managed operations through periods of peak traffic (500,000+ views/day) and successfully defended against targeted cyberattacks.
        \item Supported a 3-person editorial team by ensuring uninterrupted publishing and secure remote access.
    \end{itemize}
}
