\section{Professional Experience}

\cventry{2016--2021}{Chief Technology Officer}{The Joy of Urdu}{Lahore, Pakistan}{}{
    \begin{itemize}
        \item Directed technology strategy for a growing, decentralized nonprofit promoting Urdu literature and culture.
        \item Supported a 10-person distributed team by standardizing software use, managing licenses and access, and overseeing digital onboarding.
        \item Architected and maintained a redundant AWS-based WordPress infrastructure to ensure reliable content delivery.
    \end{itemize}
}

\cventry{2016--Present}{Director of Information Technology}{Council for Democracy and Tolerance}{Fairfax, VA}{}{
    \begin{itemize}
        \item Oversee IT infrastructure and digital tools for a U.S.-based democracy and tolerance advocacy organization.
        \item Implement cloud-based solutions to support distributed collaboration, including email, document management, and automated backups.
        \item Lead data analysis efforts for quarterly performance reviews of organizational initiatives.
    \end{itemize}
}

\cventry{2014--2016}{Chief Technology Officer}{Khabaristan Times}{Lahore, Pakistan}{}{
    \begin{itemize}
        \item Built and maintained a secure, auto-scaling AWS-backed platform for a satirical news outlet dubbed the "Onion of Pakistan."
        \item Managed operations through periods of peak traffic (500,000+ views/day) and successfully defended against targeted cyberattacks.
        \item Supported a 3-person editorial team by ensuring uninterrupted publishing and secure remote access.
    \end{itemize}
}
