\section{Professional Experience}

\cventry{2020--Present}{Graduate Research Assistant}{Cognitive Disorders Research Lab, University of Toledo}{Toledo, OH}{}{
    \begin{itemize}
        \item Led research on kinase network inference and drug repurposing in schizophrenia; co-authored 25+ peer-reviewed publications and presented at 10+ national conferences.
        \item Supervised the Schizophrenia Research Team, overseeing 8 published manuscripts during tenure.
        \item Designed and deployed lab-wide AWS infrastructure supporting 50+ researchers with scalable compute and secure access to research tools.
        \item Principal developer of three internal pipelines for transcriptomic and proteomic data analysis, significantly reducing analysis time and error rates.
        \item Mentored 5 junior researchers in computational methods, code quality, and reproducible research practices.
    \end{itemize}
}

\cventry{2017--2018}{Deputy Medical Superintendent / Medical Officer}{Chaudhary Pervaiz Elahi Institute of Cardiology}{Multan, Pakistan}{}{
    \begin{itemize}
        \item Supported hospital administration by coordinating operational reviews, resource allocation, and logistics.
        \item Oversaw the hospital's dengue screening program for six months, ensuring continuity of services during peak season.
        \item Led the development of the hospital's official introduction and history video as part of a visibility and outreach initiative.
    \end{itemize}
}

\cventry{2016--Present}{Director of Information Technology}{Council for Democracy and Tolerance}{Fairfax, VA}{}{
    \begin{itemize}
        \item Oversee IT infrastructure and digital tools for a U.S.-based democracy and tolerance advocacy organization.
        \item Implement cloud-based solutions to support distributed collaboration, including email, document management, and automated backups.
        \item Lead data analysis efforts for quarterly performance reviews of organizational initiatives.
    \end{itemize}
}
