\section{Open–Source Tools \& Projects}

\cventry{2021--Present}{\textbf{3PodReport}}{Automated Transcriptomic Analysis Report Generator}{R Markdown Framework}{\url{https://github.com/CogDisResLab/3PodReport}}{
    \begin{itemize}
        \item Generates comprehensive reports integrating drugfindR, BioPathNet, and enrichment results.
        \item Used across multiple projects in the Cognitive Disorders Research Lab.
        \item Extensible and documented; maintained as a core lab reporting tool.
    \end{itemize}
}

\cventry{2021--Present}{\textbf{aaprop}}{Amino Acid Properties REST API}{Rust Application}{\url{https://github.com/Imamiland/aaprop}}{
    \begin{itemize}
        \item High-performance REST API for physicochemical amino acid property data.
        \item Built with \emph{actix-web} in Rust; supports Shuttle and Docker deployments.
        \item Includes CLI and REST interface; 26 releases under Apache 2.0/MIT license.
        \item Live demo: \url{https://aaprop-c1io.shuttle.app/}
    \end{itemize}
}

\cventry{2022--Present}{\textbf{Variant Forge}}{Protein Sequence Comparison Service}{Web Application \& CLI}{\url{https://github.com/Imamiland/variant-forge}}{
    \begin{itemize}
        \item Calculates physicochemical distances between protein or DNA-translated amino acid sequences.
        \item Provides both web-based interface and command-line tool.
        \item Available as a REST API service and Docker image under open-source license.
        \item Under active development for improvements and web application frontend.
    \end{itemize}
}
