\section{Activism \& Community Service}

\cventry{2022--2023}{President}{Council of Biomedical Graduate Students}{Toledo, OH}{}{
    \begin{itemize}
        \item Led advocacy initiatives for biomedical graduate students.
        \item Liaised with university administration to address student concerns.
        \item Organized seasonal events for incoming and current students, including the White Coat Ceremony.
    \end{itemize}
}

\cventry{2021--2022}{President}{Graduate Student Association, University of Toledo}{Toledo, OH}{}{
    \begin{itemize}
        \item Advocated for increased graduate student funding and visibility.
        \item Organized career development workshops and research symposiums.
        \item Successfully negotiated with administration to resolve graduate student concerns regarding parking fees and space availability.
    \end{itemize}
}

\cventry{2021--2022}{Vice President}{Council of Biomedical Graduate Students}{Toledo, OH}{}{
    \begin{itemize}
        \item Supported presidential initiatives and led student advocacy efforts.
        \item Strengthened communication between students and faculty.
        \item Helped plan year-round programming for graduate students.
        \item Successfully opposed and reversed a policy that would have docked graduate student pay for minor administrative errors.
    \end{itemize}
}

\cventry{2021--2023}{Founding President}{Association of Bioinformaticists and Computational Biologists}{Toledo, OH}{}{
    \begin{itemize}
        \item Founded the University of Toledo's first student organization for computational biology.
        \item Hosted workshops and networking events for graduate students.
        \item Launched an annual regional bioinformatics hackathon.
    \end{itemize}
}

\cventry{2015--2019}{Volunteer Reading Group Coordinator}{The Joy of Urdu Reading Groups}{Multan, Pakistan}{}{
    \begin{itemize}
        \item Coordinated reading groups across the Multan region.
        \item Promoted literacy and cultural engagement through Urdu literature.
        \item Designed the group model later replicated internationally (London, Dubai, Abu Dhabi, Lahore).
    \end{itemize}
}

\cventry{2017}{Founding Member \& IT Consultant}{Alliance of Inclusive Muslims}{}{}{
    \begin{itemize}
        \item Participated in the founding conference as a representative of *Muslim World Today*.
        \item Developed a resilient and redundant website for the organization.
        \item Built a distributed internal IT system using GSuite for a remote team.
        \item Provided IT capacity-building support to member organizations.
    \end{itemize}
}

\cventry{2011--2013}{Founder \& President}{Irrtiqa}{Multan, Pakistan}{}{
    \begin{itemize}
        \item Led seminars on rationality and skepticism, titled *How to Change Your Thinking*.
        \item Conducted youth leadership camps to foster critical thinking and civic responsibility.
        \item Organized debate and essay competitions on citizenship and democracy for high school students.
    \end{itemize}
}

\cventry{2010--2013}{Founder \& President}{TEACH}{Multan, Pakistan}{}{
    \begin{itemize}
        \item Developed a presentation series titled *Human Rights Throughout the Ages*, tracing the development of the Universal Declaration of Human Rights.
        \item Delivered the series across schools and colleges in the region.
        \item Promoted human rights awareness and civic engagement through education.
    \end{itemize}
}
