\section{Activism \& Community Service}

\cventry{2022--2023}{President}{Council of Biomedical Graduate Students}{Toledo, OH}{}{
    \begin{itemize}
        \item Led advocacy initiatives for biomedical graduate students.
        \item Liaised with university administration to address student concerns.
        \item Organized seasonal events for incoming and current students, including the White Coat Ceremony.
    \end{itemize}
}

\cventry{2021--2022}{President}{Graduate Student Association, University of Toledo}{Toledo, OH}{}{
    \begin{itemize}
        \item Advocated for increased graduate student funding and visibility.
        \item Organized career development workshops and research symposiums.
        \item Successfully negotiated with administration to resolve graduate student concerns regarding parking fees and space availability.
    \end{itemize}
}

\cventry{2021--2022}{Vice President}{Council of Biomedical Graduate Students}{Toledo, OH}{}{
    \begin{itemize}
        \item Supported presidential initiatives and led student advocacy efforts.
        \item Strengthened communication between students and faculty.
        \item Helped plan year-round programming for graduate students.
        \item Successfully opposed and reversed a policy that would have docked graduate student pay for minor administrative errors.
    \end{itemize}
}

\cventry{2021--2023}{Founding President}{Association of Bioinformaticists and Computational Biologists}{Toledo, OH}{}{
    \begin{itemize}
        \item Founded the University of Toledo's first student organization for computational biology.
        \item Hosted workshops and networking events for graduate students.
        \item Launched an annual regional bioinformatics hackathon.
    \end{itemize}
}

\cventry{2019--present}{Member}{Amateur Radio Emergency Service}{Toledo, OH}{}{
    \begin{itemize}
        \item Provided support during weather-emergencies to emergency services
        \item Volunteered as a radio operator for the Glass City Marathon 2022, 2023 and 2024
        \item Volunteered as a radio operator for the Sylvania Triathlon
    \end{itemize}
}
